An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-30 VLDB2026/main.tex
Update main.tex

	Moreover, aside from BigANN, there is currently a lack of systematic evaluation specifically targeting hybrid query algorithms. To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios. Additionally, we further assess the robustness of each algorithm under varying conditions.

>>>>

	Moreover, \textcolor{blue}{beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.} To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios. Additionally, we further assess the robustness of each algorithm under varying conditions.
